Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-01-07 manuscript/draft_rsfmri.Rmd
merged changes

```{r FDFC correlation, eval=FALSE, echo=FALSE}
source("/data/pt_02161/Analysis/Preprocessing/qa/rs_qa/group_level_QA/QC_FC_correlations/calc_qc_fc_correlations.R")
FDFC=calc_qc_fc(final)
write.csv(FDFC,"./report/FDFCcorrelations.csv", row.names = FALSE)
```

```{r figNetworks, echo=FALSE, out.width="49%", out.height="30%", fig.cap="Resting state networks based on AROMA+CC+GSR input data, one-sample t-tests adjusting for age and sex over all timepoints and participants with bootstrapped clusterwise inference (p FWE<0.05)", fig.subcap=c("DMN seeded from precuneus", "Reward network seeded from Nucleus Accumbens"),fig.show='hold',fig.align='center'}
networks=c("../report/DMN_thresholded_for_clusterFWE005.png","../report/Rew_thresholded_for_clusterFWE005.png")
knitr::include_graphics(networks)
```

@@

```{r figtSNR,fig.cap="Lower tSNR in the region of interest NAcc versus precuneus used for seed-based connectivity (shown are all 101 timepoints)", out.width="60%",  echo=FALSE}
p
```
Yet, the reward network was less pronounced (overall lower T-values) and symmetric (no significant connectivity with left amygdala), which might be due to lower SNR in the seeded brain region (see Figure \@ref{fig:figtSNR}.

>>>>

```{r FDFC correlation, eval=FALSE, echo=FALSE}
# do not evaluate if saved already
source("/data/pt_02161/Analysis/Preprocessing/qa/rs_qa/group_level_QA/QC_FC_correlations/calc_qc_fc_correlations.R")
FDFC=calc_qc_fc(final)
write.csv(FDFC,"./report/FDFCcorrelations.csv", row.names = FALSE)
```

```{r figNetworks, echo=FALSE, out.width="49%", out.height="30%", fig.cap="Resting state networks based on AROMA+CC+GSR input data, one-sample t-tests adjusting for age and sex over all timepoints and participants with bootstrapped clusterwise inference (p FWE<0.05)", fig.subcap=c("DMN seeded from precuneus", "Reward network seeded from Nucleus Accumbens"),fig.show='hold',fig.align='center'}
#setwd(knitr::opts_knit$get("root.dir"))
networks = c("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/DMN_thresholded_for_clusterFWE005.png",
             "/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/Rew_thresholded_for_clusterFWE005.png")
knitr::include_graphics(networks)
```

@@

```{r figtSNR,fig.cap="Lower tSNR in the region of interest NAcc versus precuneus used for seed-based connectivity (shown are all 101 timepoints)", out.width="60%", fig.align="center", echo=FALSE}
p
```
Yet, the reward network was less pronounced (overall lower T-values) and symmetric (no significant connectivity with left amygdala), which might be due to lower SNR in the seeded brain region (see Figure \@ref{fig:figtSNR}.
